\par\centerline {\bf Calibration}
{\eightpoint\begintt
calapply ... lgm  ... Apply gain and passband corrections producing calibrated data 
calfit ..... pjt  ... Fit polynomial to amp/phase data 
calflag .... pjt  ... Display raw calibration data with user interaction 
calflux .... jm   ... Print flux data for a calibrator source. 
calib ...... pjt  ... Display raw calibration data with user interaction 
\endtt}
{\eightpoint\begintt
callist .... pjt  ... List items from calibration data set 
calmake .... pjt  ... Create cal file from observation of calibrator 
passfit .... lgm  ... Fit polynomials to a passband calibration set 
passmake ... lgm  ... Create passband calibration set 
selfcal .... mchw ... Determine self-calibration of calibration gains. 
\endtt}
{\eightpoint\begintt
tvflag ..... jm   ... Interactive editing of a UV data set on a TV device. 
uvaflag .... bpw  ... Use flags in one uv database to set flags in another 
uvedit ..... jm   ... Editing of the baseline of a UV data set. 
uvflag ..... bpw  ... Flags or unflags uv data 
\endtt}
\par\centerline {\bf Data Transfer}
{\eightpoint\begintt
fits ....... rjs  ... Conversion between MIRIAD and FITS image and uv formats 
hatmap ..... mchw ... Convert old Hat Creek 2D images to MIRIAD cube 
hcconv ..... pjt  ... Convert Hat Creek uv format into MIRIAD uv format 
uvhat ...... wh   ... Convert Hat Creek uv format into MIRIAD uv format 
\endtt}
\par\centerline {\bf Deconvolution}
{\eightpoint\begintt
clean ...... mchw ... Apply Hogbom, Clark or Steer CLEAN algorithm to a map 
maxen ...... rjs  ... Maximum Entropy deconvolution 
restore .... mchw ... Restore clean components to make the CLEAN map 
tvcln ...... mchw ... Clark/Steer CLEAN with display of intermediates 
\endtt}
\par\centerline {\bf General}
{\eightpoint\begintt
(none)
\endtt}
\par\centerline {\bf Map Analysis}
{\eightpoint\begintt
convol ..... mchw ... Convolve a cube with a "beam function" 
ellint ..... mchw ... Integrate a Miriad image in elliptical annuli. 
hermes ..... mchw ... Make model images for Mercury. 
histo ...... mchw ... Find statistics of image and plot simple histogram 
imlist ..... mchw ... List items and pixel values from an image 
\endtt}
{\eightpoint\begintt
implot ..... mchw ... Multi-panel contour or grey scale plot of a Miriad Image. 
imspect .... mchw ... Make spectrum from a Miriad image.
imwrite .... mchw ... Make a Miriad Image from a foreign dataset.
moment ..... mchw ... Calculate moments of a Miriad image. 
shifty ..... rjs  ... Align two images. 
\endtt}
\par\centerline {\bf Map Combination}
{\eightpoint\begintt
contsub .... bpw  ... Subtract continuum map from vxy cube by spectral fitting 
imcat ...... mchw ... Concatenate several images to one cube 
linmos ..... mchw ... Linear mosaicing of datacubes 
maths ...... pjt  ... Mathematical operations on images and image data 
odnh3 ...... pjt  ... Ammonia analysis program 
\endtt}
\par\centerline {\bf Map Making}
{\eightpoint\begintt
fft ........ mchw ... Fourier transform on image(s) 
invert ..... rjs  ... Transform visibility data into a map 
selfcal .... mchw ... Determine self-calibration of calibration gains. 
uvgen ...... mchw ... Compute visibilities for a model source. 
uvpoint .... mchw ... Generate artifial mosaiced observation 
\endtt}
\par\centerline {\bf Map Manipulation}
{\eightpoint\begintt
convol ..... mchw ... Convolve a cube with a "beam function" 
demos ...... mchw ... Inverse mosaicing operation 
imgen ...... mchw ... All-purpose image manipulator/creator 
imsub ...... mchw ... Extract subportion of an image 
maths ...... pjt  ... Mathematical operations on images and image data 
\endtt}
{\eightpoint\begintt
odnh3 ...... pjt  ... Ammonia analysis program 
reorder .... mchw ... Interchange the axes of a cube 
\endtt}
\vfill\eject
\par\centerline {\bf Model Fitting}
{\eightpoint\begintt
zeestat .... nebk ... Fits Zeeman parameters to I and V cubes 
\endtt}
\par\centerline {\bf Plotting}
{\eightpoint\begintt
boxspec .... bpw  ... Write spectra (from vxy cube) as text file 
cgplot ..... nebk ... Makes contour and grey scale plots 
implot ..... mchw ... Multi-panel contour or grey scale plot of a Miriad Image. 
tvflag ..... jm   ... Interactive editing of a UV data set on a TV device. 
uvplt ...... mchw ... Plot visibility amplitude or phase versus time or uv-distance. 
\endtt}
{\eightpoint\begintt
uvspect .... mchw ... Plot visibility amplitude/phase vs velocity 
varlist .... lgm  ... List all variables in dataset 
varplot .... lgm  ... Plot uv variables 
velplot .... mchw ... Interactive task to Average, Graph, and Extract Miriad Images. 
\endtt}
\par\centerline {\bf Profile Analysis}
{\eightpoint\begintt
zeeeta ..... nebk ... Compute Zeeman parameter eta 
zeefake .... nebk ... Generate fake Zeeman data. 
zeemap ..... nebk ... Map the magnetic field from I and V cubes 
zeesim ..... nebk ... Test reliability of Zeeman splitting errors 
\endtt}
\par\centerline {\bf Tools}
{\eightpoint\begintt
doc ........ bpw  ... MIRIAD documentation program 
flint ...... rjs  ... Fortran source code verifier 
miriad ..... pjt  ... General program to run miriad programs 
mirtool .... pjt  ... MIRIAD SunView interface (SUN only) 
panel ...... jm   ... Control panel program 
\endtt}
{\eightpoint\begintt
ratty ...... bpw  ... FORTRAN preprocessor, so that same code works on more machines 
\endtt}
\par\centerline {\bf Utility}
{\eightpoint\begintt
boxspec .... bpw  ... Write spectra (from vxy cube) as text file 
copyhd ..... rjs  ... Copy items from one data-set to another. 
corset ..... jm   ... Program that models correlator setups. 
delhd ...... rjs  ... Delete a data-set item. 
imgen ...... mchw ... All-purpose image manipulator/creator 
\endtt}
{\eightpoint\begintt
imhead ..... jm   ... List items and pixel values from an image. 
itemize .... pjt  ... List information about image dataset 
listobs .... lgm  ... Makes a summary of a set of observations. 
maths ...... pjt  ... Mathematical operations on images and image data 
prthis ..... bpw  ... List history item of a dataset 
\endtt}
{\eightpoint\begintt
puthd ...... pjt  ... Change the value of or add a header item 
varlist .... lgm  ... List all variables in dataset 
\endtt}
\par\centerline {\bf uv Analysis}
{\eightpoint\begintt
fft ........ mchw ... Fourier transform on image(s) 
fitgains ... mchw ... List gains for a uv dataset 
gainerr .... rjs  ... Add dummy gains to a visibility file. 
uvcat ...... rjs  ... Concatenate and copy uv datasets into one; apply gains file, selec
uvcheck .... mchw ... Check uvdata selection and uv-variable values. 
\endtt}
{\eightpoint\begintt
uvcover .... lgm  ... Display uv coverage 
uvdisplay .. lgm  ... Suntools display header information about uv dataset 
uvflag ..... bpw  ... Flags or unflags uv data 
uvgen ...... mchw ... Compute visibilities for a model source. 
uvindex .... mchw ... Scan a uvdata file, and note when uvvariables change. 
\endtt}
{\eightpoint\begintt
uvlist ..... mchw ... Print data values from uv dataset 
uvmodel .... mchw ... Add, subtract, etc, a model from a uv data set. 
uvplot ..... mchw ... Plot selected uvdata variables and linetypes versus time.
uvplt ...... mchw ... Plot visibility amplitude or phase versus time or uv-distance. 
uvpoint .... mchw ... Generate artifial mosaiced observation 
\endtt}
{\eightpoint\begintt
uvspect .... mchw ... Plot visibility amplitude/phase vs velocity 
uvtrack .... mchw ... Plot u-v tracks for n configurations of m antennas 
varplot .... lgm  ... Plot uv variables 
\endtt}
\par\centerline {\bf Visual Display}
{\eightpoint\begintt
msss ....... jm   ... MIRIAD version of the AIPS Sun Screen Server (SUN only) 
tvall ...... jm   ... Interact with a previously displayed image 
tvdisp ..... jm   ... Display an image on a TV device 
tvinit ..... rjs  ... Initialize a TV device 
views ...... bpw  ... Generate a projection of the datacube 
\endtt}
\par\centerline {\bf Other}
{\eightpoint\begintt
avmaths .... nebk ... Operate on cube with averaged plane from cube 
hatfft ..... mchw ... Timing and test of fft algorithms. 
imdiff ..... rjs  ... Shift and expand an image to make it match another. 
smooth ..... nebk ... Convolve an image (in the image domain) with a gaussian. 
tpgains .... mchw ... Estimate antenna gains from total power measurements. 
\endtt}
{\eightpoint\begintt
uvputhd .... lgm  ... Allows user to alter values of header variables in uv dataset 
\endtt}
