{\eightpoint\begintt
avmaths ..... nebk ... Operate on cube with averaged plane from cube 
boxspec ..... bpw  ... Write spectra (from vxy cube) as text file 
calapply .... lgm  ... Apply gain and passband corrections producing calibrated data
calfit ...... pjt  ... Fit polynomial to amp/phase data 
calflag ..... pjt  ... Display raw calibration data with user interaction 
\endtt}
{\eightpoint\begintt
calflux ..... jm   ... Print flux data for a calibrator source. 
calib ....... pjt  ... Display raw calibration data with user interaction 
callist ..... pjt  ... List items from calibration data set 
calmake ..... pjt  ... Create cal file from observation of calibrator 
cgplot ...... nebk ... Makes contour and grey scale plots 
\endtt}
{\eightpoint\begintt
clean ....... mchw ... Apply Hogbom, Clark or Steer CLEAN algorithm to a map 
contsub ..... bpw  ... Subtract continuum map from vxy cube by spectral fitting 
convol ...... mchw ... Convolve a cube with a "beam function" 
copyhd ...... rjs  ... Copy items from one data-set to another. 
corset ...... jm   ... Program that models correlator setups. 
\endtt}
{\eightpoint\begintt
delhd ....... rjs  ... Delete a data-set item. 
demos ....... mchw ... Inverse mosaicing operation 
doc ......... bpw  ... MIRIAD documentation program 
ellint ...... mchw ... Integrate a Miriad image in elliptical annuli. 
fft ......... mchw ... Fourier transform on image(s) 
\endtt}
{\eightpoint\begintt
fitgains .... mchw ... List gains for a uv dataset 
fits ........ rjs  ... Conversion between MIRIAD and FITS image and uv formats 
flint ....... rjs  ... Fortran source code verifier 
gainerr ..... rjs  ... Add dummy gains to a visibility file. 
hatfft ...... mchw ... Timing and test of fft algorithms. 
\endtt}
{\eightpoint\begintt
hatmap ...... mchw ... Convert old Hat Creek 2D images to MIRIAD cube 
hcconv ...... pjt  ... Convert Hat Creek uv format into MIRIAD uv format 
hermes ...... mchw ... Make model images for Mercury. 
histo ....... mchw ... Find statistics of image and plot simple histogram 
imcat ....... mchw ... Concatenate several images to one cube 
\endtt}
{\eightpoint\begintt
imdiff ...... rjs  ... Shift and expand an image to make it match another. 
imgen ....... mchw ... All-purpose image manipulator/creator 
imhead ...... jm   ... List items and pixel values from an image. 
imlist ...... mchw ... List items and pixel values from an image 
implot ...... mchw ... Multi-panel contour or grey scale plot of a Miriad Image.
\endtt}
{\eightpoint\begintt
imspect ..... mchw ... Make spectrum from a Miriad image. 
imsub ....... mchw ... Extract subportion of an image 
imwrite ..... mchw ... Make a Miriad Image from a foreign dataset.
invert ...... rjs  ... Transform visibility data into a map 
itemize ..... pjt  ... List information about image dataset 
\endtt}
{\eightpoint\begintt
linmos ...... mchw ... Linear mosaicing of datacubes 
listobs ..... lgm  ... Makes a summary of a set of observations. 
maths ....... pjt  ... Mathematical operations on images and image data 
maxen ....... rjs  ... Maximum Entropy deconvolution 
miriad ...... pjt  ... General program to run miriad programs 
\endtt}
{\eightpoint\begintt
mirtool ..... pjt  ... MIRIAD SunView interface (SUN only) 
moment ...... mchw ... Calculate moments of a Miriad image. 
msss ........ jm   ... MIRIAD version of the AIPS Sun Screen Server (SUN only) 
odnh3 ....... pjt  ... Ammonia analysis program 
panel ....... jm   ... Control panel program 
\endtt}
{\eightpoint\begintt
passfit ..... lgm  ... Fit polynomials to a passband calibration set 
passmake .... lgm  ... Create passband calibration set 
prthis ...... bpw  ... List history item of a dataset 
puthd ....... pjt  ... Change the value of or add a header item 
ratty ....... bpw  ... FORTRAN preprocessor, so that same code works on more machines 
\endtt}
{\eightpoint\begintt
reorder ..... mchw ... Interchange the axes of a cube 
restore ..... mchw ... Restore clean components to make the CLEAN map 
selfcal ..... mchw ... Determine self-calibration of calibration gains. 
shifty ...... rjs  ... Align two images. 
smooth ...... nebk ... Convolve an image (in the image domain) with a gaussian. 
\endtt}
{\eightpoint\begintt
tpgains ..... mchw ... Estimate antenna gains from total power measurements. 
tvall ....... jm   ... Interact with a previously displayed image 
tvcln ....... mchw ... Clark/Steer CLEAN with display of intermediates 
tvdisp ...... jm   ... Display an image on a TV device 
tvflag ...... jm   ... Interactive editing of a UV data set on a TV device. 
\endtt}
{\eightpoint\begintt
tvinit ...... rjs  ... Initialize a TV device 
uvaflag ..... bpw  ... Use flags in one uv database to set flags in another 
uvcat ....... rjs  ... Concatenate and copy uv datasets into one; apply gains file, sele 
uvcheck ..... mchw ... Check uvdata selection and uv-variable values. 
uvcover ..... lgm  ... Display uv coverage 
\endtt}
{\eightpoint\begintt
uvdisplay ... lgm  ... Suntools display header information about uv dataset 
uvedit ...... jm   ... Editing of the baseline of a UV data set. 
uvflag ...... bpw  ... Flags or unflags uv data 
uvgen ....... mchw ... Compute visibilities for a model source. 
uvhat ....... wh   ... Convert Hat Creek uv format into MIRIAD uv format 
\endtt}
{\eightpoint\begintt
uvindex ..... mchw ... Scan a uvdata file, and note when uvvariables change. 
uvlist ...... mchw ... Print data values from uv dataset 
uvmodel ..... mchw ... Add, subtract, etc, a model from a uv data set. 
uvplot ...... mchw ... Plot selected uvdata variables and linetypes versus time.
uvplt ....... mchw ... Plot visibility amplitude or phase versus time or uv-distance. 
\endtt}
{\eightpoint\begintt
uvpoint ..... mchw ... Generate artifial mosaiced observation 
uvputhd ..... lgm  ... Allows user to alter values of header variables in uv dataset
uvspect ..... mchw ... Plot visibility amplitude/phase vs velocity 
uvtrack ..... mchw ... Plot u-v tracks for n configurations of m antennas 
varlist ..... lgm  ... List all variables in dataset 
\endtt}
{\eightpoint\begintt
varplot ..... lgm  ... Plot uv variables 
velplot ..... mchw ... Interactive task to Average, Graph, and Extract Miriad Images. 
views ....... bpw  ... Generate a projection of the datacube 
zeeeta ...... nebk ... Compute Zeeman parameter eta 
zeefake ..... nebk ... Generate fake Zeeman data. 
\endtt}
{\eightpoint\begintt
zeemap ...... nebk ... Map the magnetic field from I and V cubes 
zeesim ...... nebk ... Test reliability of Zeeman splitting errors 
zeestat ..... nebk ... Fits Zeeman parameters to I and V cubes 
\endtt}
