\par\centerline {\bf bpw - Bart Wakker}
{\eightpoint\begintt
boxspec ..... bpw  ... Write spectra (from vxy cube) as text file 
contsub ..... bpw  ... Subtract continuum map from vxy cube by spectral fitting 
doc ......... bpw  ... MIRIAD documentation program 
prthis ...... bpw  ... List history item of a dataset 
ratty ....... bpw  ... FORTRAN preprocessor, so that same code works on more machines 
\endtt}
{\eightpoint\begintt
uvaflag ..... bpw  ... Use flags in one uv database to set flags in another 
uvflag ...... bpw  ... Flags or unflags uv data 
views ....... bpw  ... Generate a projection of the datacube 
\endtt}
\par\centerline {\bf jm - Jim Morgan}
{\eightpoint\begintt
calflux ..... jm   ... Print flux data for a calibrator source. 
corset ...... jm   ... Program that models correlator setups. 
imhead ...... jm   ... List items and pixel values from an image. 
msss ........ jm   ... MIRIAD version of the AIPS Sun Screen Server (SUN only) 
panel ....... jm   ... Control panel program 
\endtt}
{\eightpoint\begintt
tvall ....... jm   ... Interact with a previously displayed image 
tvdisp ...... jm   ... Display an image on a TV device 
tvflag ...... jm   ... Interactive editing of a UV data set on a TV device. 
uvedit ...... jm   ... Editing of the baseline of a UV data set. 
\endtt}
\par\centerline {\bf lgm - Lee Mundy}
{\eightpoint\begintt
calapply .... lgm  ... Apply gain and passband corrections producing calibrated data
listobs ..... lgm  ... Makes a summary of a set of observations. 
passfit ..... lgm  ... Fit polynomials to a passband calibration set 
passmake .... lgm  ... Create passband calibration set 
uvcover ..... lgm  ... Display uv coverage 
\endtt}
{\eightpoint\begintt
uvdisplay ... lgm  ... Suntools display header information about uv dataset 
uvputhd ..... lgm  ... Allows user to alter values of header variables in uv dataset
varlist ..... lgm  ... List all variables in dataset 
varplot ..... lgm  ... Plot uv variables 
\endtt}
\par\centerline {\bf mchw - Mel Wright}
{\eightpoint\begintt
clean ....... mchw ... Apply Hogbom, Clark or Steer CLEAN algorithm to a map 
convol ...... mchw ... Convolve a cube with a "beam function" 
demos ....... mchw ... Inverse mosaicing operation 
ellint ...... mchw ... Integrate a Miriad image in elliptical annuli. 
fft ......... mchw ... Fourier transform on image(s) 
\endtt}
{\eightpoint\begintt
fitgains .... mchw ... List gains for a uv dataset 
hatfft ...... mchw ... Timing and test of fft algorithms. 
hatmap ...... mchw ... Convert old Hat Creek 2D images to MIRIAD cube 
hermes ...... mchw ... Make model images for Mercury. 
histo ....... mchw ... Find statistics of image and plot simple histogram 
\endtt}
{\eightpoint\begintt
imcat ....... mchw ... Concatenate several images to one cube 
imgen ....... mchw ... All-purpose image manipulator/creator 
imlist ...... mchw ... List items and pixel values from an image 
implot ...... mchw ... Multi-panel contour or grey scale plot of a Miriad Image.
imspect ..... mchw ... Make spectrum from a Miriad image. 
\endtt}
{\eightpoint\begintt
imsub ....... mchw ... Extract subportion of an image 
imwrite ..... mchw ... Make a Miriad Image from a foreign dataset.
linmos ...... mchw ... Linear mosaicing of datacubes 
moment ...... mchw ... Calculate moments of a Miriad image. 
reorder ..... mchw ... Interchange the axes of a cube 
\endtt}
{\eightpoint\begintt
restore ..... mchw ... Restore clean components to make the CLEAN map 
selfcal ..... mchw ... Determine self-calibration of calibration gains. 
tpgains ..... mchw ... Estimate antenna gains from total power measurements. 
tvcln ....... mchw ... Clark/Steer CLEAN with display of intermediates 
uvcheck ..... mchw ... Check uvdata selection and uv-variable values. 
\endtt}
{\eightpoint\begintt
uvgen ....... mchw ... Compute visibilities for a model source. 
uvindex ..... mchw ... Scan a uvdata file, and note when uvvariables change. 
uvlist ...... mchw ... Print data values from uv dataset 
uvmodel ..... mchw ... Add, subtract, etc, a model from a uv data set. 
uvplot ...... mchw ... Plot selected uvdata variables and linetypes versus time.
\endtt}
{\eightpoint\begintt
uvplt ....... mchw ... Plot visibility amplitude or phase versus time or uv-distance. 
uvpoint ..... mchw ... Generate artifial mosaiced observation 
uvspect ..... mchw ... Plot visibility amplitude/phase vs velocity 
uvtrack ..... mchw ... Plot u-v tracks for n configurations of m antennas 
velplot ..... mchw ... Interactive task to Average, Graph, and Extract Miriad Images. 
\endtt}
\par\centerline {\bf nebk - Neil Killeen}
{\eightpoint\begintt
avmaths ..... nebk ... Operate on cube with averaged plane from cube 
cgplot ...... nebk ... Makes contour and grey scale plots 
smooth ...... nebk ... Convolve an image (in the image domain) with a gaussian. 
zeeeta ...... nebk ... Compute Zeeman parameter eta 
zeefake ..... nebk ... Generate fake Zeeman data. 
\endtt}
{\eightpoint\begintt
zeemap ...... nebk ... Map the magnetic field from I and V cubes 
zeesim ...... nebk ... Test reliability of Zeeman splitting errors 
zeestat ..... nebk ... Fits Zeeman parameters to I and V cubes 
\endtt}
\par\centerline {\bf pjt - Peter Teuben}
{\eightpoint\begintt
calfit ...... pjt  ... Fit polynomial to amp/phase data 
calflag ..... pjt  ... Display raw calibration data with user interaction 
calib ....... pjt  ... Display raw calibration data with user interaction 
callist ..... pjt  ... List items from calibration data set 
calmake ..... pjt  ... Create cal file from observation of calibrator 
\endtt}
{\eightpoint\begintt
hcconv ...... pjt  ... Convert Hat Creek uv format into MIRIAD uv format 
itemize ..... pjt  ... List information about image dataset 
maths ....... pjt  ... Mathematical operations on images and image data 
miriad ...... pjt  ... General program to run miriad programs 
mirtool ..... pjt  ... MIRIAD SunView interface (SUN only) 
\endtt}
{\eightpoint\begintt
odnh3 ....... pjt  ... Ammonia analysis program 
puthd ....... pjt  ... Change the value of or add a header item 
\endtt}
\par\centerline {\bf rjs - Bob Sault}
{\eightpoint\begintt
copyhd ...... rjs  ... Copy items from one data-set to another. 
delhd ....... rjs  ... Delete a data-set item. 
fits ........ rjs  ... Conversion between MIRIAD and FITS image and uv formats 
flint ....... rjs  ... Fortran source code verifier 
gainerr ..... rjs  ... Add dummy gains to a visibility file. 
\endtt}
{\eightpoint\begintt
imdiff ...... rjs  ... Shift and expand an image to make it match another. 
invert ...... rjs  ... Transform visibility data into a map 
maxen ....... rjs  ... Maximum Entropy deconvolution 
shifty ...... rjs  ... Align two images. 
tvinit ...... rjs  ... Initialize a TV device 
\endtt}
{\eightpoint\begintt
uvcat ....... rjs  ... Concat., copy uv DS's into one; apply gains file, sele 
\endtt}
\par\centerline {\bf wh - Wilson Hoffman}
{\eightpoint\begintt
uvhat ....... wh   ... Convert Hat Creek uv format into MIRIAD uv format 
\endtt}
