{\eightpoint\begintt
addhist ..... pjt .... Add history to a dataset 
addpoly ..... pjt .... Add a polynomial to the database of polynomials 
amphase ..... pjt .... Compute amplitude and phase. 
ampscal ..... pjt .... Scale amplitudes of a calibrator 
angles ...... mchw ... Convert angle in degrees/hours to a string 
\endtt}
{\eightpoint\begintt
arctan ...... bpw .... Arctangent function 
aricomp ..... pjt .... Parse a Fortran-like expression. 
ariexec ..... pjt .... Evalute an expression, previously parsed by AriComp. 
assert ...... pjt .... Assert a condition, otherwise bug out 
assertf ..... pjt .... Assert a file existence condition, otherwise bug out 
\endtt}
{\eightpoint\begintt
asserti2 .... pjt .... Assert a condition, otherwise bug out 
atod ........ bpw .... Convert a string into a double precision. 
atoi ........ bpw .... Convert a string into an integer. 
axistype .... mchw ... Find the axis label and plane value in user friendly units 
basant ...... jm ..... Routine to determine antennas from baseline number. 
\endtt}
{\eightpoint\begintt
binfid ...... nebk ... Adjust window size and fiddle bin sizes for spacial avg'ing 
binrd2 ...... nebk ... For vxy images, apply specified binning criterion 
binup ....... nebk ... Bin up data in array 
blname ...... pjt .... Returns baseline name 
boxes ....... mjs .... Summary of region of interest routines. 
\endtt}
{\eightpoint\begintt
boxinfo ..... mjs .... Determine bounding box of the region of interest. 
boxinput .... mjs .... Read command line box specification. 
boxmask ..... mjs .... AND in a mask to the region of interest. 
boxnr ....... bpw .... Find in which box the input value lies. 
boxrect ..... mjs .... Determine in a region-of-interest is rectangular. 
\endtt}
{\eightpoint\begintt
boxruns ..... mjs .... Return region of interest in "runs" form. 
boxset ...... mjs .... Set default region of interest. 
bselect ..... mchw ... Find if given antenna is in given baseline code 
bsrcha ...... mchw ... Search a list of strings for a particular string. 
bsrchi ...... mchw ... Search a list of integers for a particular integer. 
\endtt}
{\eightpoint\begintt
bug ......... mjs .... Give an error message, and abort if needed. 
bugno ....... mjs .... Give a error message associated with a particular error number. 
caclose ..... pjt .... Close a calibration set 
cadread ..... pjt .... Read data from a calibration set 
cadwrite .... pjt .... Write data into a calibration set 
\endtt}
{\eightpoint\begintt
caerror ..... pjt .... Write a calibration I/O error 
caflag ...... pjt .... Flag data in a calibration set 
calget ...... jm ..... Routine to retrieve an interpolated calibrator flux. 
caopen ...... pjt .... Open a calibration set 
casread ..... pjt .... Read source index data 
\endtt}
{\eightpoint\begintt
caswrite .... pjt .... Write source index data 
chkpoly ..... pjt .... Check if the current polynomial is set 
code2s ...... pjt .... Convert ascii code to integer slot code 
convl ....... mjs .... Performs the convolution of the image with the beam. 
convlini .... mjs .... Initialize the convolution routines. 
\endtt}
{\eightpoint\begintt
corrfun ..... mchw ... Generate the gridding convolution correction function. 
ctrl ........ jm ..... Manipulating a control panel. 
ctrlchck .... jm ..... Check if a particular buttons has been pushed. 
ctrlclr ..... jm ..... Clear any memory in the control panel of buttons being pressed. 
ctrldef ..... jm ..... Define a control panel button, etc. 
\endtt}
{\eightpoint\begintt
ctrlfin ..... jm ..... Close down the control panel. 
ctrlinit .... jm ..... Initialise the panel panel. 
ctrlopen .... jm ..... Open the panel panel. 
ctrlset ..... jm ..... Set the value of a control panel button, etc. 
ctrlview .... jm ..... Pop up the control panel on the workstation screen. 
\endtt}
{\eightpoint\begintt
ctrlwait .... jm ..... Wait for a button to be pressed. 
dangle ...... jm ..... Convert degrees/hours value into a formatted string. 
dayjul ...... jm ..... Format a conventional calendar day into a Julian day. 
deghms ...... bpw .... Write out ra and dec in hms/dms from input in degrees 
delay ....... mjs .... Delay a specified length of time. 
\endtt}
{\eightpoint\begintt
delim ....... bpw .... Make sure value is between limits 
display ..... jm ..... Load a map onto a TV device with user specified ranges. 
dtoa ........ bpw .... Convert a double precision value into a string. 
enuff ....... bpw .... Page output. 
equals ...... bpw .... Check if input equals of a number of possible strings 
\endtt}
{\eightpoint\begintt
evalpoly .... pjt .... Evaluate a polynomial 
expi ........ mchw ... Extract complex exponent of input in radians 
fatpoint .... pjt .... Draw fat, visible points 
fftcc ....... rjs .... Complex to complex 1D FFT routine. 
fftcr ....... rjs .... Complex to real 1D FFT routine. 
\endtt}
{\eightpoint\begintt
fftrc ....... rjs .... Real to complex 1D FFT 
filedel ..... pjt .... Delete a file 
findbase .... pjt .... Returns the baseline number 
findname .... jm ..... Return the expanded name of a file. 
findsrc ..... pjt .... Find index of word in a list of words 
\endtt}
{\eightpoint\begintt
fitcdio ..... rjs .... Sequential read or write of a FITS header. 
fitpoly ..... pjt .... Fit a polynomial 
fitrdhda .... rjs .... Read a character value from a FITS file header. 
fitrdhdd .... rjs .... Read a double precision value from a FITS file header. 
fitrdhdi .... rjs .... Read an integer value from a FITS file header. 
\endtt}
{\eightpoint\begintt
fitrdhdl .... rjs .... Read a logical value from a FITS file header. 
fitrdhdr .... rjs .... Read a real value from a FITS file header. 
fitsrch ..... rjs .... Search for a keyword in the header of an old FITS file. 
fitwrhda .... rjs .... Write a string to a FITS file header. 
fitwrhdd .... rjs .... Write a double precision keyword to a FITS file header. 
\endtt}
{\eightpoint\begintt
fitwrhdh .... rjs .... Write a string to a FITS file header. 
fitwrhdi .... rjs .... Write an integer value to a FITS file header. 
fitwrhdl .... rjs .... Write a logical value to a FITS file header. 
fitwrhdr .... rjs .... Write a real value to a FITS file header. 
flipper ..... lgm .... Flip phases into a continuous string 
\endtt}
{\eightpoint\begintt
freelun ..... mjs .... Release a logical unit, previously allocated with GetLun.
fullname .... bpw .... Expand an environment variable in front of a filename 
fuvclose .... rjs .... Close a UV FITS file. 
fuvopen ..... rjs .... Open a FITS uv file. 
fuvrdhd ..... rjs .... Get coordinate information about a UV FITS file. 
\endtt}
{\eightpoint\begintt
fuvread ..... rjs .... Read visibility data from UV FITS file. 
fuvsetlm .... rjs .... Set the ranges of parameters for a FITS UV file. 
fuvtoff ..... rjs .... Get time offset for a UV FITS file. 
fuvwrhd ..... rjs .... Save UV FITS file coordinate information. 
fuvwrite .... rjs .... Write data to a UV FITS file. 
\endtt}
{\eightpoint\begintt
fxyclose .... rjs .... Close a FITS image file. 
fxyopen ..... rjs .... Open a FITS image file. 
fxyread ..... rjs .... Read a row of data from a FITS image. 
fxysetlm .... rjs .... Set the pixel range for scaling a FITS image. 
fxysetpl .... rjs .... Select the plane of interest in a FITS image. 
\endtt}
{\eightpoint\begintt
fxywrite .... rjs .... Write a row of a FITS image. 
gainfact .... mchw ... Determine the self-cal gain at a given time and baseline.
gainfin ..... mchw ... Close up the selfcal gains routines. 
gaininit .... mchw ... Initialise the "gains" routines. 
gaus ........ rjs .... Generate gaussianly distributed random variables. 
\endtt}
{\eightpoint\begintt
gcffun ...... mchw ... Generate the gridding convolution function. 
getants ..... pjt .... Returns the number of antennas and antenna pair 
getbeam ..... mchw ... Get beam from image header. 
getclo3 ..... lgm .... Return sign for closure calculation for 3 baselines 
getfield .... bpw .... Extract a field from a string. 
\endtt}
{\eightpoint\begintt
getlun ...... mjs .... Get a logical unit number. 
getparm ..... bpw .... Extract a parameter from a string. 
getpb ....... mchw ... Determine the primary beam associated with a image. 
getplane .... mjs .... Read portion of a plane, specified by runs format. 
getpoly ..... pjt .... Read in the phase-amplitude calibration fit 
\endtt}
{\eightpoint\begintt
getslot ..... pjt .... Get all slots that match wildcard slotcode 
gettok ...... bpw .... Extract a token from a string. 
haccess ..... mjs .... Open an item of a data set for access. 
hangle ...... jm ..... Convert hours value (in radians) into a formatted string.
hannsm ...... jm ..... Hanning smooth a data array.. 
\endtt}
{\eightpoint\begintt
hclose ...... mjs .... Close a Miriad data set. 
hcoeffs ..... jm ..... Calculated coefficients for Hanning smoothing. 
hdaccess .... mjs .... Finish up access to an item. 
hdcopy ...... mjs .... Copy a headfer variable from one data set to another. 
hdelete ..... mjs .... Delete an item from a data-set. 
\endtt}
{\eightpoint\begintt
hdprobe ..... mjs .... Determine characteristics of a header variable. 
hdprsnt ..... mjs .... Determine if a header variable is present. 
hisappn ..... pjt .... Append history from a file to an open dataset 
hisclose .... mjs .... This closes the history file. 
hisinput .... jm ..... Copy task input parameters to a history file. 
\endtt}
{\eightpoint\begintt
hisopen ..... mjs .... Open the history file. 
hisread ..... mjs .... Read a line of text from the history file. 
hiswrite .... mjs .... Write a line of text to the history file. 
hopen ....... mjs .... Open a data set. 
hread ....... mjs .... Hwrite -- Read and write items. 
\endtt}
{\eightpoint\begintt
hsize ....... mjs .... Determine the size (in bytes) of an item. 
hsorta ...... jm ..... Perform an index heapsort on a character string array. 
hsortad ..... jm ..... Perform a dual index heapsort on a character string array.
hsortar ..... jm ..... Perform a dual index heapsort on a character string array.
hsortd ...... jm ..... Perform an indexed heapsort on a double precision array. 
\endtt}
{\eightpoint\begintt
hsorti ...... jm ..... Perform an indexed heapsort on a integer array. 
hsortr ...... jm ..... Perform an indexed heapsort on a real array. 
hsortrr ..... jm ..... Perform a dual index heapsort on a real array. 
imminmax .... jm ..... Return Miriad image minimum and maximum value. 
imscale ..... jm ..... Autoscale a map. 
\endtt}
{\eightpoint\begintt
indek ....... bpw .... Get position of substring in a string, returning length if not fo 
inipoly ..... pjt .... Forced initialize polynomials 
intpini ..... mjs .... Initialize the interpolation i/o routines. 
intprd ...... mjs .... Read a row of interpolated data 
intprini .... mjs .... Reinitialize the interpolation i/o routines. 
\endtt}
{\eightpoint\begintt
isalnum ..... bpw .... Return true if char is an alphanumeric character 
isalpha ..... bpw .... Return true if char is a letter (a-z, A-Z) 
iscoords .... bpw .... Test if input string can represent coordinates and convert it 
isdigit ..... bpw .... Return true if char is 0, 1, 2, 3, 4, 5, 6, 7, 8 or 9 
islower ..... bpw .... Return true if char is a lowercase letter (a-z) 
\endtt}
{\eightpoint\begintt
ismax ....... pjt .... Return index of maximum value of a real array. 
ismin ....... pjt .... Return index of minimum value of a real array. 
isrchfge .... pjt .... Search real vector for target. 
isrchfgt .... pjt .... Search real vector for target. 
isrchfle .... pjt .... Search real vector for target. 
\endtt}
{\eightpoint\begintt
isrchflt .... pjt .... Search real vector for target. 
isrchieq .... pjt .... Search integer vector for target. 
isrchige .... pjt .... Search integer vector for target. 
isrchigt .... pjt .... Search integer vector for target. 
isrchile .... pjt .... Search integer vector for target. 
\endtt}
{\eightpoint\begintt
isrchilt .... pjt .... Search integer vector for target. 
isrchine .... pjt .... Search integer vector for target. 
isupper ..... bpw .... Return true if char is an uppercase letter (A-Z) 
itime ....... rjs .... Returns the present date. 
itoa ........ bpw .... Convert an integer into a string. 
\endtt}
{\eightpoint\begintt
j1xbyx ...... mchw ... Calculate j1(x)/x 
julday ...... jm ..... Format a Julian day into a conventional calendar day. 
keya ........ pjt .... Retrieve a character string from the command line. 
keyd ........ pjt .... Retrieve a double precision from the command line. 
keyf ........ pjt .... Retrieve a filename string (with wildcards) from the command line 
\endtt}
{\eightpoint\begintt
keyfin ...... pjt .... Finish access to the 'key' routines. 
keyi ........ pjt .... Retrieve an integer from the command line. 
keyini ...... pjt .... Initialise the `key' routines. 
keyl ........ pjt .... Retrieve a logical value from the command line 
keyprsnt .... pjt .... Determine if a keyword is present on the command line. 
\endtt}
{\eightpoint\begintt
keyr ........ pjt .... Retrieve a real value from the command line. 
lcase ....... bpw .... Convert a string to lower case. 
len1 ........ bpw .... Determine the unpadded length of a character string. 
linetype .... bpw .... Read standard linetype keyword and transfer information to uvio 
linlsq ...... bpw .... Return parameters of a straight line fit 
\endtt}
{\eightpoint\begintt
llsqu ....... bpw .... Linear least squares fitting 
logclose .... bpw .... Finish up with the log file. 
logopen ..... bpw .... Initialise the log file routines. 
logwrit ..... bpw .... Write a line to the log file. 
logwrite .... bpw .... Write a line to the log file. 
\endtt}
{\eightpoint\begintt
lsqfill ..... pjt .... Add sums-of-squares to least squares matrix 
match ....... bpw .... Check if a string occurs in a list of valid strings 
matchdcd .... bpw .... Check if a string occurs in a list of valid strings, with extras 
miniflip .... lgm .... Flip phases into a continuous string 
mitoa ....... bpw .... Convert many integers into a string. 
\endtt}
{\eightpoint\begintt
mkeya ....... pjt .... Retrieve multiple character values from the command line.
mkeyf ....... pjt .... Retrieve multiple filenames. 
mkeyi ....... pjt .... Retrieve multiple integer values from the command line. 
mkeyr ....... pjt .... Retrieve multiple real values from the command line. 
model ....... mchw ... Calculate model visibilities, given a model image. 
\endtt}
{\eightpoint\begintt
modelini .... mchw ... Ready the uv data file for processing by the Model routine. 
nel ......... bpw .... Return the number used values in an array 
nelc ........ bpw .... Return the length of the string 
nextpow2 .... mchw ... Find the next power of two. 
nfig ........ bpw .... Find number of digits in a number 
\endtt}
{\eightpoint\begintt
nllsqu ...... bpw .... Nonlinear least squares fitting 
oneamp ...... mchw ... Convert visibility to amp/phase or real/imag 
options ..... bpw .... Get command line options. 
output ...... bpw .... Output a line of text to the user. 
packi2 ...... mjs .... Pack normal integers into 16 bit integers 
\endtt}
{\eightpoint\begintt
padleft ..... bpw .... Right justify a string to length characters. 
pgerase ..... pjt .... Erase the screen - and nothing more 
pghline ..... mchw ... Histogram line plot for pgplot. 
phase ....... mchw ... Extract phase in radians from complex number 
phaseamp .... pjt .... Convert to phase/amplitude 
\endtt}
{\eightpoint\begintt
phasedis .... pjt .... Find consistent antenna phases 
phiwrap ..... pjt .... Returns the number of 2pi wraps 
plotone ..... lgm .... Plot one or more set of x,y points on a single graph 
powell ...... bpw .... Minimization of a function, without derivative information. 
prime ....... jm ..... Returns a prime less than or equal to N. 
\endtt}
{\eightpoint\begintt
progname .... pjt .... Return name of the program currently running 
prompt ...... bpw .... Read input from the user 
putplane .... mjs .... Writes a portion of a plane, specified by runs format. 
putpoly ..... pjt .... Write out the phase-amplitude calibration fit 
putruns ..... mjs .... Writes the blanking file of an image. 
\endtt}
{\eightpoint\begintt
putsrc ...... pjt .... Write out source stuff 
pxtotv ...... jm ..... Convert image pixels to TV device positions. 
r8tyx ....... mchw ... Radix, 8 iterations 
radhms ...... bpw .... Write out ra and dec in hms/dms from input in radians 
randset ..... rjs .... Set random number generator seed. 
\endtt}
{\eightpoint\begintt
rangle ...... jm ..... Convert degrees value (in radians) into a formatted string. 
rdhda ....... mjs .... Read a string-valued header variable. 
rdhdc ....... mjs .... Read a complex-valued header variable. 
rdhdd ....... mjs .... Read a double precision-valued header variable. 
rdhdi ....... mjs .... Read an integer-valued header variable. 
\endtt}
{\eightpoint\begintt
rdhdia ...... pjt .... Read an integer array header variable 
rdhdr ....... mjs .... Read a real-valued header variable. 
readbrk ..... pjt .... Read breakpoint data 
readset ..... pjt .... Read in data from a calibration set 
remext ...... bpw .... Remove the extension part of a filename 
\endtt}
{\eightpoint\begintt
rfac ........ jm ..... Calculate n factorial. 
rpolyzr ..... bpw .... Roots of a real polynomial. 
rtfmt ....... bpw .... Construct a format during run time 
rtoa ........ bpw .... Convert a real value into a string. 
s2code ...... pjt .... Convert integer slot code to 4 character slot code 
\endtt}
{\eightpoint\begintt
scalunit .... pjt .... Set calibration unit conversion mode 
scanchar .... bpw .... Scan a string for a character. 
scrclose .... mjs .... Close and delete a scratch file. 
scropen ..... mjs .... Open a scratch file. 
scrread ..... mjs .... Read real data from a scratch file. 
\endtt}
{\eightpoint\begintt
scrwrite .... mjs .... Write real data to the scratch file. 
selapply .... bpw .... Call the appropraite uv routine to set the uv selection. 
selinput .... bpw .... Get the users uv selection specification. 
selprobe .... bpw .... Check if a particular uv data has been selected. 
setsflag .... pjt .... Set flags along time axis according to selected sources 
\endtt}
{\eightpoint\begintt
sfetra ...... bpw .... Transformation between equatorial and other coordinate systems 
shadowed .... bpw .... ... 
solve ....... pjt .... Solve a matrix 
sortidxa .... pjt .... Index sort of a an array of character values 
sortidxd .... pjt .... Index sort of a an array of double precision values 
\endtt}
{\eightpoint\begintt
sortidxi .... pjt .... Index sort of a an array of integer values 
sortidxr .... pjt .... Index sort of a an array of real values 
spanchar .... bpw .... Skip over a particular character. 
squares ..... pjt .... Compute sums-of-squares 
substr ...... bpw .... Returns the n-th substring from the input string 
\endtt}
{\eightpoint\begintt
tabflux ..... jm ..... Return the flux of a calibrator source at an input freq. 
taver ....... pjt .... Scalar averaging an array 
teken ....... bpw .... Returns the sign of a real value 
title ....... mchw ... Write title in standard format into LogFile. 
todayjul .... jm ..... Format the current day into a Julian day. 
\endtt}
{\eightpoint\begintt
token ....... mchw ... Obtain token delimited by _ ()[] 
trnfin ...... mchw ... Close up the transpose routines. 
trnini ...... mchw ... Initialise the transpose routines. 
trnread ..... mchw ... Read back a plane of the reordered cube. 
trnwrite .... mchw ... Write a plane of the cube in its initial order. 
\endtt}
{\eightpoint\begintt
tvchan ...... jm ..... Display a given image channel. 
tvchar ...... jm ..... Get characteristics of the display device. 
tvclose ..... jm ..... Close the display device. 
tvcursor .... jm ..... Read the location of the image display device's cursor. 
tveras ...... jm ..... Erase a channel on the image display device. 
\endtt}
{\eightpoint\begintt
tvflush ..... jm ..... Flush data to the display device. 
tvline ...... jm ..... Write a raster line to the image display device. 
tvlocal ..... jm ..... Put the display device into an interactive loop with the user. 
tvlut ....... jm ..... Load a image display device's lookup table. 
tvopen ...... jm ..... Open an image display device. 
\endtt}
{\eightpoint\begintt
tvreset ..... jm ..... Reset the image display device. 
tvscrl ...... jm ..... Scroll a display on a TV device. 
tvselpt ..... jm ..... Interactive point/range selection on a display device. 
tvtext ...... jm ..... Write a character string to the image display device. 
tvtopx ...... jm ..... Convert TV device position to image pixels. 
\endtt}
{\eightpoint\begintt
tvview ...... jm ..... Change the viewing window to a subportion of image memory.
tvwind ...... jm ..... Set/read current window (viewport) of a display device. 
tvzoom ...... jm ..... Zoom a region of an image on a TV device. 
txtclose .... bpw .... Close a text file 
txtopen ..... bpw .... Open a text file 
\endtt}
{\eightpoint\begintt
txtopena .... nebk ... Open a text file for appendation. 
txtread ..... bpw .... Read a line from a text file 
txtwrite .... bpw .... Write a line to a text file 
ucase ....... bpw .... Convert string to upper case. 
ucursor ..... mjs .... Check Ultra cursor pos and 'exit' button state. 
\endtt}
{\eightpoint\begintt
udef ........ mjs .... Set up and display Ultra control panel. 
ufin ........ mjs .... Finish Ultra frame buffer and control panel. 
uinit ....... mjs .... Indicate to ultra where control panel host is. 
ulocal ...... mjs .... Allow user to fiddle the ultra frame buffer. 
uniform ..... rjs .... Return uniformly distributed random variables. 
\endtt}
{\eightpoint\begintt
unpacki2 .... mjs .... Unpack 16 bit integers into normal integers 
uvclose ..... rjs .... Close a uv file 
uvcopyvr .... rjs .... Copy variables from one uv file to another. 
uvdatget .... mchw ... Get information about the UVDat routines. 
uvdatinp .... mchw ... Get command line uv data parameters. 
\endtt}
{\eightpoint\begintt
uvdatprb .... mchw ... Determine what data have been selected in the uvdat routines. 
uvdatrd ..... mchw ... Read uv data from a multi-file set. 
uvfit1 ...... mchw ... Fit a constant to an "object" returned by uvinfo. 
uvfit2 ...... mchw ... Fit a line to an "object" returned by uvinfo. 
uvflgwr ..... rjs .... Write uv flags after a read. 
\endtt}
{\eightpoint\begintt
uvgetvr ..... rjs .... Get the values of a uv variable. 
uvinfo ...... rjs .... Get information about the last data read with uvread. 
uvnext ...... rjs .... Skip to the next uv record. 
uvopen ...... rjs .... Open a uv data file. 
uvprobvr .... rjs .... Return information about a variable. 
\endtt}
{\eightpoint\begintt
uvputvr ..... rjs .... Write the value of a uv variable. 
uvrdvr ...... rjs .... Return the value of a UV variable. 
uvread ...... rjs .... Read in some uv correlation data. 
uvrewind .... rjs .... Reset the uv data file to the start of the file. 
uvscan ...... rjs .... Scan a uv file until a variable changes. 
\endtt}
{\eightpoint\begintt
uvselect .... rjs .... Select or reject uv data. 
uvset ....... rjs .... Set up the uv linetype, and other massaging steps. 
uvtrack ..... rjs .... Set flags and switches associated with a uv variable. 
uvupdate .... rjs .... Check whether any "important" variables have changed. 
uvwdatrd .... mchw ... Read wideband correlator data. 
\endtt}
{\eightpoint\begintt
uvwread ..... rjs .... Read in the wideband uv correlation data. 
uvwrite ..... rjs .... Write correlation data to a uv file. 
uvwwrite .... rjs .... Write wide-band correlation data to a uv file. 
vectav ...... pjt .... Vector averaging with lookup index table 
wedge ....... jm ..... Load a wedge onto a TV device with user specified ranges.
\endtt}
{\eightpoint\begintt
whenfeq ..... pjt .... Return locations equal to target. 
whenfge ..... pjt .... Return locations greater than or equal to the target. 
whenfgt ..... pjt .... Return locations greater than the target. 
whenfle ..... pjt .... Return locations less than or equal to the target. 
whenflt ..... pjt .... Return locations less than the target. 
\endtt}
{\eightpoint\begintt
whenfne ..... pjt .... Return locations not equal to target. 
whenige ..... pjt .... Return locations greater than or equal to the integer target. 
whenigt ..... pjt .... Return locations greater than the integer target. 
whenile ..... pjt .... Return locations less than or equal to the integer target.
whenilt ..... pjt .... Return locations less than the target. 
\endtt}
{\eightpoint\begintt
width ....... mchw ... Calculate wideband channel width 
win ......... pjt .... Subroutine package for interactive plots, using PGPLOT. 
wincoord .... pjt .... Change PGPLOT coordinates to a window 
wincurs ..... pjt .... Get a character from a window 
winloc ...... pjt .... Set window screen locations 
\endtt}
{\eightpoint\begintt
winnear ..... pjt .... Return the nearest point 
winnorm ..... pjt .... Normalize plots and add a margin 
winnormy .... pjt .... Normalize plots and add a margin 
winpick ..... pjt .... Set the active windows 
winpick1 .... pjt .... Set an active window 
\endtt}
{\eightpoint\begintt
winpoint .... pjt .... Draw points 
winqscal .... pjt .... Queries set window user scales for selected window 
winscale .... pjt .... Set window user scales 
winscalx .... pjt .... Set window user X-scales 
winscaly .... pjt .... Set window user Y-scales 
\endtt}
{\eightpoint\begintt
winset ...... pjt .... Set max unzoomed window matrix 
winshow ..... pjt .... Put the plots onto the screen 
winsize ..... pjt .... Size windows to the data 
winsymb ..... pjt .... Return win2pgplot symbol marker 
wintoscr .... pjt .... Convert a point to screen coordinates 
\endtt}
{\eightpoint\begintt
wintousr .... pjt .... Convert a point to screen coordinates 
wrhda ....... mjs .... Write a string-valued header variable. 
wrhdc ....... mjs .... Write a complex-valued header variable. 
wrhdd ....... mjs .... Write a double precision valued header variable. 
wrhdi ....... mjs .... Write an integer valued header variable. 
\endtt}
{\eightpoint\begintt
wrhdia ...... pjt .... Write an integer array header variable 
wrhdr ....... mjs .... Write a real valued header variable. 
writbrk ..... pjt .... Write break point data 
writeset .... pjt .... Write out data to a calibration set (timesorted) 
writflag .... pjt .... Write out flags to a calibration data set 
\endtt}
{\eightpoint\begintt
xyclose ..... mjs .... Close up an image file. 
xyflgrd ..... mjs .... Read image masking information (flags format). 
xyflgwr ..... mjs .... Write image masking information (flags format). 
xymkrd ...... mjs .... Read the masking information for an image (runs format). 
xymkwr ...... mjs .... Write image masking information (runs format). 
\endtt}
{\eightpoint\begintt
xyopen ...... mjs .... Open an image file. 
xyread ...... mjs .... Read a row from an image. 
xysetpl ..... mjs .... Set which plane of a cube is to be accessed. 
xywrite ..... mjs .... Write a row to an image. 
zed ......... nebk ... Zeeman fit of I spectrum to V spectrum. 
\endtt}
{\eightpoint\begintt
zedfudge .... nebk ... Calculate sigma fudge factor, for Zeeman experiments. 
zedfunc ..... nebk ... Return Zeeman maximum likelihood chi**2 value. 
zedihat ..... nebk ... Calculate Zeeman estimate of a true I spectrum 
zedrho ...... nebk ... Estimate Zeeman splitting, for spectrally correlated noise. 
zedscale .... nebk ... Determine conversion factor from channels to magnetic field. 
\endtt}
{\eightpoint\begintt
zedvhat ..... nebk ... Calculate Zeeman estimate of a true V spectrum 
\endtt}
