
\par This chapter lists LINPACK subroutines compiled into {\bf Miriad's}
own LINPACK library (liblinpack.a).  All source code is in FORTRAN,
and is not processed by {\bf Miriad's} RATTY preprocessor.  Refer to
the LINPACK manual for a fuller description of the subroutines, and
for a specification of the calling sequence.

{\eightpoint\begintt
CBLAS     COMPLEX VERSION OF THE BASIC LINEAR ALGEBRA ROUTINES
DBLAS     DOUBLE PRECISION VERSION OF THE BASIC LINEAR ALGEBRA ROUTINES
SBLAS     SINGLE PRECISION VERSION OF THE BASIC LINEAR ALGEBRA ROUTINES
\endtt}
{\eightpoint\begintt
PXXYY     GENERIC NAME OF A LINPACK ROUTINE. THE LETTERS HAVE
          THE FOLLOWING MEANINGS
  
          P - SIGNIFIES TYPE AND PRECISION OF THE DATA
  
              S = ROUTINE IS REAL SINGLE PRECISION
              D = ROUTINE IS REAL DOUBLE PRECISION
              C = ROUTINE IS COMPLEX SINGLE PRECISION
              Z = ROUTINE IS COMPLEX DOUBLE PRECISION (IBM VERSION ONLY)
  
          XX - SIGNIFIES TYPE OF MATRIX HANDLED
  
               GE = GENERAL FULL MATRIX
               GB = GENERAL BAND MATRIX
               PO = POSITIVE DEFINITE
               PP = POSITIVE DEFINITE PACKED
               PB = POSITIVE DEFINITE BAND
               TR = TRIANGULAR
               GT = GENERAL TRIDIAGONAL
               PT = POSITIVE DEFINITE TRIDIAGONAL
               SI = SYMMETRIC INDEFINITE
               SP = SYMMETRIC INDEFINITE PACKED
               HI = HERMITIAN INDEFINITE
               HP = HERMITIAN INDEFINITE PACKED
               CH = CHOLESKY DECOMPOSITION
               QR = ORTHOGONAL TRIANGULAR DECOMPOSITION
               SV = SINGULAR VALUE DECOMPOSITION
  
          YY - SIGNIFIES TYPE OF OPERATION PERFORMED
  
               FA = FACTOR
               CO = FACTOR AND ESTIMATE CONDITION
               DC = DECOMPOSE
               SL = SOLVE
               DI = DETERMINANT, INVERSE, INERTIA
               UD = UPDATE
               DD = DOWNDATE
               EX = EXCHANGE
\endtt}
\vfill
\eject

{\eightpoint\begintt
SGECO     FACTOR AND ESTIMATE CONDITION OF A GENERAL MATRIX
DGECO
CGECO
\endtt}
{\eightpoint\begintt
SGEFA     FACTOR A GENERAL MATRIX (NO CONDITION NUMBER RETURNED)
DGEFA
CGEFA
\endtt}
{\eightpoint\begintt
SGESL     SOLVE A LINEAR SYSTEM AFTER FACTORING
DGESL
CGESL
\endtt}
{\eightpoint\begintt
SGEDI     COMPUTE DETERMINANT/INVERSE/INERTIA OF A GENERAL MATRIX
DGEDI
CGEDI
\endtt}
{\eightpoint\begintt
SGBCO     FACTOR & ESTIMATE CONDITION OF GENERAL BANDED MATRIX
DGBCO
CGBCO
\endtt}
{\eightpoint\begintt
SGBFA     FACTOR GENERAL BAND MATRIX (NO CONDITION RETURNED)
DGBFA
CGBFA
\endtt}
{\eightpoint\begintt
SGBSL     SOLVE GENERAL BAND SYSTEM AFTER FACTORING
DGBSL
CGBSL
\endtt}
{\eightpoint\begintt
SGBDI     COMPUTE DETERMINANT/INVERSE/INERTIA OF GENERAL BAND MATRIX
DGBDI
CGBDI
\endtt}
{\eightpoint\begintt
SPOCO     FACTOR & ESTIMATE CONDITION OF POS. DEF. SYMM. MATRIX
DPOCO
\endtt}
{\eightpoint\begintt
SPOFA     FACTOR A POS. DEF. SYMM. MATRIX (NO CONDITION RETURNED)
DPOFA
\endtt}
{\eightpoint\begintt
SPOSL     SOLVE A POS. DEF. SYMM. SYSTEM AFTER FACTORING
DPOSL
\endtt}
{\eightpoint\begintt
SPODI     DETERMINANT/INVERSE/INERTIA OF POS. DEF. SYMM. MATRIX
DPODI
\endtt}
{\eightpoint\begintt
SPPCO     FACTOR & EST. CONDITION OF "PACKED" POS. DEF. SYMM. MATRIX
DPPCO
\endtt}
{\eightpoint\begintt
SPPFA     FACTOR A "PACKED" POS. DEF. SYMM. MATRIX (NO CONDITION RETURNE
DPPFA
\endtt}
{\eightpoint\begintt
SPPSL     SOLVE A "PACKED" POS. DEF. SYMM. SYSTEM AFTER FACTORING
DPPSL
\endtt}
{\eightpoint\begintt
SPBCO     FACTOR & EST. CONDITION OF POS. DEF. SYMM. BAND MATRIX
DPBCO
\endtt}
{\eightpoint\begintt
SPBFA     FACTOR A POS. DEF. SYMM. BAND MATRIX (NO CONDITION RETURNED)
DPBFA
\endtt}
{\eightpoint\begintt
SPBSL     SOLVE A POS. DEF. SYMM. BAND SYSTEM AFTER FACTORING
DPBSL
\endtt}
{\eightpoint\begintt
SPBDI     DETERMINANT/INVERSE/INERTIA OF POS. DEF. SYMM. BAND MATRIX
DPBDI
\endtt}
{\eightpoint\begintt
SSICO     FACTOR & EST. CONDITION OF A SYMMETRIC MATRIX
DSICO
CSICO
\endtt}
{\eightpoint\begintt
SSIFA     FACTOR A SYMMETRIC MATRIX (NO CONDITION RETURNED)
DSIFA
CSIFA
\endtt}
{\eightpoint\begintt
SSISL     SOLVE A SYMMETRIC SYSTEM AFTER FACTORING
DSISL
CSISL
\endtt}
{\eightpoint\begintt
SSIDI     DETERMINANT/INVERSE/INERTIA OF SYMMETRIC MATRIX
DSIDI
CSIDI
\endtt}
{\eightpoint\begintt
SSPCO     FACTOR & EST. CONDITION OF "PACKED" SYMMETRIC MATRIX
DSPCO
CSPCO
\endtt}
{\eightpoint\begintt
SSPFA     FACTOR A "PACKED" SYMMETRIC MATRIX (NO CONDITION RETURNED)
DSPFA
CSPFA
\endtt}
{\eightpoint\begintt
SSPSL     SOLVE A "PACKED" SYMMETRIC SYSTEM
DSPSL
CSPSL
\endtt}
{\eightpoint\begintt
SSPDI     DETERMINANT/INVERSE/INERTIA OF A "PACKED" SYMMETRIC MATRIX
DSPDI
CSPDI
\endtt}
{\eightpoint\begintt
CHICO     FACTOR AND EST. CONDITION OF A HERMITIAN MATRIX
CHIFA     FACTOR A HERMITIAN MATRIX (NO CONDITION RETURNED)
CHISL     SOLVE A HERMITIAN SYSTEM AFTER FACTORING
CHIDI     DETERMINANT/INVERSE/INERTIA OF A HERMITIAN MATRIX
CHPCO     FACTOR & EST. CONDITION OF A "PACKED" HERMITIAN MATRIX
CHPFA     FACTOR A "PACKED" HERMITIAN MATRIX (NO CONDITION RETURNED)
CHPSL     SOLVE A "PACKED" HERMITIAN SYSTEM AFTER FACTORING
CHPDI     DETERMINANT/INVERSE/INERTIA OF A "PACKED" HERMITIAN MATRIX
\endtt}
{\eightpoint\begintt
STRCO     FACTOR & EST. CONDITION OF A TRIANGULAR MATRIX
DTRCO
CTRCO
\endtt}
{\eightpoint\begintt
STRSL     SOLVE A TRIANGULAR SYSTEM
DTRSL
CTRSL
\endtt}
{\eightpoint\begintt
STRDI     DETERMINANT/INVERSE/INERTIA OF A TRIANGULAR MATRIX
DTRDI
CTRDI
\endtt}
{\eightpoint\begintt
SGTSL     SOLVE A TRIDIAGONAL SYSTEM
DGTSL
CGTSL
\endtt}
{\eightpoint\begintt
SPTSL     SOLVE A POS. DEF. SYMM. TRIDIAGONAL SYSTEM
DPTSL
\endtt}
{\eightpoint\begintt
SCHDC     CHOLESKY DECOMPOSITION OF A POS. DEF. SYMM. MATRIX
DCHDC
\endtt}
{\eightpoint\begintt
SQRDC     "QR" DECOMPOSITION OF A RECTANGULAR MATRIX
DQRDC
\endtt}
{\eightpoint\begintt
SQRSL     SOLVE LEAST SQUARES USING OUTPUT OF SQRDC (DQRDC)
DQRDC
\endtt}
{\eightpoint\begintt
SCHUD     UPDATE A CHOLESKY DECOMPOSITION
DCHUD
\endtt}
{\eightpoint\begintt
SCHDD     DOWDATE A CHOLESKY DECOMPOSITION
\endtt}
{\eightpoint\begintt
SCHEX     UPDATE A CHOLESKY DECOMPOSITION AFTER ROW/COLUMN PERMUTATION
DCHEX
\endtt}
{\eightpoint\begintt
SSVDC     SINGULAR VALUE DECOMPOSITION
DSVDC
\endtt}
