%------------------------------------------------------------------------
% Appendix - MIRIAD Environment Variables
%------------------------------------------------------------------------
%  History
%
%  --mar91 mjs  Original version.
%  23jun91 mjs  Added WIPHELP for WIP program; alphabetized list.
%
%------------------------------------------------------------------------

The following list gives a brief description of each of the standard
MIRIAD environment variables.
\vskip .2in  

{\raggedright
\tabskip=0em
\halign{#\tabskip=2em&#\hfil\cr

MIR&The home directory of the MIRIAD system.\cr
&\cr
MIRBIN&The binary directory containing MIRIAD executables.\cr
      &\$MIR/bin/sun4 on a sun4, \$MIR/bin/sun3 on a sun3, etc.\cr
&\cr
MIRCAT&A directory for files needed by MIRIAD programs.\cr
      &\$MIR/cat\cr
&\cr
MIRDEF&Default directory to place ``lastexit'' file.\cr
      &Generally the current working directory.\cr
&\cr
MIRDOC&The directory containing MIRIAD on-line docs.\cr
      &\$MIR/doc\cr
&\cr
MIRHELLO&Set at logon as a ``motd'' switch.\cr
&\cr
MIRHOST&The host hardware (sun3, sun4, u2, vms, convex).\cr
&\cr
MIRINC&The directory containing general MIRIAD include files.\cr
      &\$MIR/src/inc\cr
&\cr
MIRLIB&The binary directory containing MIRIAD libraries.\cr
      &\$MIR/lib/sun4 on a sun4, \$MIR/lib/sun3 on a sun3, etc.\cr
&\cr
MIRLOG&Log file for MIRIAD programs.\cr
      &/tmp/\$USER.mirlog\cr
&\cr
MIRLPGP&PGPLOT library to use in loading programs.\cr
       &\$MIRLIB/libpgplot.a, or installation-set.\cr
&\cr
MIRLXDS&Installation's directory for X-libraries (or null string).\cr
       &/usr/local/lib (at Illinois).\cr
       &/usr/lib (at Maryland).\cr
&\cr
MIRNEWS&Placeholder for future MIRIAD ``news'' feature.\cr
       &\$MIR/news\cr
&\cr
MIRPAGER&Used in presenting formatted on-line docs.\cr
        &doc\cr
&\cr
MIRPDOC&The directory containing on-line docs for executables.\cr
      &\$MIR/doc/prog\cr
&\cr
MIRPROG&Source code for programs resides here.\cr
       &\$MIR/src/prog\cr
&\cr
MIRSAVE&Allow ``test'' systems to remember the ``production'' system.\cr
       &The production \$MIR.\cr
&\cr
MIRSDOC&The directory containing on-line docs for subroutines.\cr
      &\$MIR/doc/subs\cr
&\cr
MIRSRC&All MIRIAD source code resides here.\cr
      &\$MIR/src\cr
&\cr
MIRSUBS&Source code for subroutines resides here.\cr
       &\$MIR/subs\cr
&\cr
MIRSW&``p'' to compile with optimization, or ``t'' for debugging.\cr
&\cr
MIRXLIB&Installation's ``libX11.a'' file (or null string).\cr
       &/usr/openwin/lib/libX11.a (at Berkeley Sun4).\cr
       &/usr/local/lib/libX11.a (at Illinois Sun4).\cr
       &-lX11 (at Maryland Sun3 and Sun4).\cr
       &/usr/lib/libX11.a (at NCSA's Cray 2).\cr
       &/usr/lib/libX11.a (at NCSA's Convex).\cr
&\cr
&\cr
&\cr
&\cr
WIPHELP&Help file for MIRIAD's WIP program.\cr
       &\$MIR/src/spec/wip/wiphelp.dat\cr
&\cr
PGPLOT\_FONT&PGPLOT's grfont.dat file (see \$MIRLPGP definition).\cr
           &\$MIRLIB/grfont.dat\cr
}
}
