%------------------------------------------------------------------------
% Appendix - MIRIAD Directories
%------------------------------------------------------------------------
%  History
%
%  --mar91 mjs  Original version.
%  23jun91 mjs  Added directories for WIP program.
%
%------------------------------------------------------------------------

The following gives a brief description of each of the standard MIRIAD
directories.  It is given in a UNIX notation, but the equivalent VMS
directory names are the obvious translations.

Much disagreement, some of it good natured, has taken place over what
MIRIAD's directory structure should look like.  The structure given
below might be considered a ``standard'', but there are local variations
(mostly small) at the various MIRIAD sites.  The general rule is
``what works for you is legal, but the fewer differences, the better'':
the critical directories are {\bf \$MIR/src} and {\bf \$MIR/cat}, which
must be maintained in a manner so as to ensure the smooth transmission
of source code when tarfiles are transmitted to the various sites (the
tarfiles update specific code in specific directories, all done by
name).  Non-volatile directories (manuals and borrowed code) change too
infrequently to merit strict controls, and the contents of most other
directories are loaded on-site and never transmitted.

The entire structure is intended to be usable on all supported machines.
Empty directories (e.g., the \$MIR/bin/u2 directory at a Sun site) require
little space, and installations supporting different hardware (e.g., both
Sun3 and Sun4) need this subdirectory structure for executables and 
libraries.

The {\bf \$MIR/cat} directory originated with the need to store catalogues of
calibrators, plus other related information.  Unfortunately, it has become
a repository for needed files that don't really fit anywhere else.

MIRIAD's home directory is {\bf \$MIR}.  It is commonly the home
directory of the local MIRIAD account, though this is not required.
Subdirectories under {\bf \$MIR} are:
\vskip .2in  
\tabskip=.5em plus2em minus.5em
\halign{#&#&#&#\hfil\cr

adm/&\ldrfill&\ldrfill&For administrative use.\cr
\ldrfill&import/&\ldrfill&A place for imported tarfiles.\cr
\ldrfill&export/&\ldrfill&A place for exported tarfiles.\cr
\ldrfill&submit/&\ldrfill&A place for submitted code.\cr
bin/&\ldrfill&\ldrfill&Binaries (executables).\cr
\ldrfill&sun3/&\ldrfill&The binary directory for Sun3s.\cr
\ldrfill&sun4/&\ldrfill&The binary directory for Sun4s.\cr
\ldrfill&u2/&\ldrfill&The binary directory for Cray2.\cr
\ldrfill&vms/&\ldrfill&The binary directory for VMS.\cr
\ldrfill&convex/&\ldrfill&The binary directory for Convex.\cr
borrow/&\ldrfill&\ldrfill&Borrowed code.\cr
\ldrfill&hdf/&\ldrfill&HDF subroutines.\cr
\ldrfill&linpack/&\ldrfill&LINPACK subroutines.\cr
\ldrfill&pgplot/&\ldrfill&PGPLOT subroutines.\cr
cat/&\ldrfill&\ldrfill&Catalogues of calibrators, et. al.\cr
doc/&\ldrfill&\ldrfill&Volatile documentation.\cr
\ldrfill&prog/&\ldrfill&Programs, scripts, and commands.\cr
\ldrfill&subs/&\ldrfill&Subroutines.\cr
\ldrfill&misc/&\ldrfill&Anything else.\cr
lib/&\ldrfill&\ldrfill&Internal libraries (*.a files).\cr
\ldrfill&sun3/&\ldrfill&Sun3 libraries.\cr
\ldrfill&sun4/&\ldrfill&Sun4 libraries.\cr
\ldrfill&u2/&\ldrfill&Cray2 libraries.\cr
\ldrfill&vms/&\ldrfill&vms libraries.\cr
\ldrfill&convex/&\ldrfill&Convex libraries.\cr
manuals/&\ldrfill&\ldrfill&Paper documentation.\cr
\ldrfill&covers/&\ldrfill&PostScript files for MIRIAD manual covers.\cr
\ldrfill&eguide/&\ldrfill&MIRIAD Executable Modules.\cr
\ldrfill&hdf/&\ldrfill&HDF manual.\cr
\ldrfill&linpack/&\ldrfill&LINPACK documentation.\cr
\ldrfill&mxds/&\ldrfill&MIRIAD XDS manual.\cr
\ldrfill&pgplot/&\ldrfill&PGPLOT manual.\cr
\ldrfill&pguide/&\ldrfill&MIRIAD Programmer's Guide.\cr
\ldrfill&sguide/&\ldrfill&MIRIAD Subroutine Library.\cr
\ldrfill&uguide/&\ldrfill&MIRIAD User's Guide and Cookbook.\cr
news/&\ldrfill&\ldrfill&Future ``news'' facility.\cr
oldsrc/&\ldrfill&\ldrfill&A place to back off old source.\cr
src/&\ldrfill&\ldrfill&Main source code directory.\cr
\ldrfill&inc/&\ldrfill&Universally available include files.\cr
\ldrfill&prog/&\ldrfill&Tasks.\cr
\ldrfill&\ldrfill&analysis/&Analysis.\cr
\ldrfill&\ldrfill&calib/&Calibration.\cr
\ldrfill&\ldrfill&convert/&Data conversion.\cr
\ldrfill&\ldrfill&deconv/&Deconvolution.\cr
\ldrfill&\ldrfill&disp/&TV and plotting programs.\cr
\ldrfill&\ldrfill&map/&Mapping, mosaicing.\cr
\ldrfill&\ldrfill&misc/&Miscellaneous.\cr
\ldrfill&\ldrfill&vis/&General visibility handling.\cr
\ldrfill&subs/&\ldrfill&Universally available subroutines.\cr
\ldrfill&spec/&\ldrfill&Tasks requiring ``special'' handling to load.\cr
\ldrfill&\ldrfill&mxds/&MIRIAD version of NCSA's XDS.\cr
\ldrfill&\ldrfill&msss/&MIRIAD version of AIPS' SSS.\cr
\ldrfill&\ldrfill&hcconv/&Convert ``newhat'' RALINT data (Sun).\cr
\ldrfill&\ldrfill&uvdisplay/&Display uv Data under SunView.\cr
\ldrfill&\ldrfill&uvhat/&Convert RALINT data (VMS).\cr
   &   &      &Convert ``oldhat'' RALINT data (UNIX).\cr
\ldrfill&\ldrfill&wip/&Interactive graphics program (using PGPLOT).\cr
   &   &      &Subdirectory structure is below.\cr
\ldrfill&\ldrfill&\ldrfill&wipdoc/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/branch/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/cpgsrc/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/drivers/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/images/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/include/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/interact/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/plot/\cr
\ldrfill&\ldrfill&\ldrfill&wipsrc/sysdepunix/\cr
\ldrfill&scripts/&\ldrfill&Scripts and Commands.\cr
\ldrfill&\ldrfill&sun/&Sun scripts.\cr
\ldrfill&\ldrfill&u2/&Cray2 scripts.\cr
\ldrfill&\ldrfill&vms/&vms commands.\cr
\ldrfill&\ldrfill&convex/&Convex commands.\cr
\ldrfill&tools/&\ldrfill&Tools.\cr
testdata/&\ldrfill&\ldrfill&A place for test data.\cr
tmp/&\ldrfill&\ldrfill&Internal ``tmp'' directory.\cr
}
